On the spatial aggregation of ecosystem condition indicators

### 2025-09-12 manuscript/manuscript.qmd
start table

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
```

@@

|   | Example | Main illustrating point |
|-------------|---------------------|--------------------------------------|
| 1 | Bilberry | Commensurable spatial scales for variable and reference levels (@sec-match) |
| 2 | Wolves | Spatial compensation and discrepancy between variable and indicator (@sec-discrep) |
| 3 | PTI | Compensation and the order of operations (@sec-pathways) |
| 4 | Glaciers | Aggregation commutativity and alternative indicator weights (@sec-comp) |

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(flextable)
library(ftExtra)
```

@@

|   | Example | Main illustrating point |
|------------|------------|------------------------------------------------|
| 1 | Bilberry | Commensurable spatial scales for variable and reference levels (@sec-match) |
| 2 | Wolves | Spatial compensation and discrepancy between variable and indicator (@sec-discrep) |
| 3 | PTI | Compensation and the order of operations (@sec-pathways) |
| 4 | Glaciers | Aggregation commutativity and alternative indicator weights (@sec-comp) |
